Best Practices for Developing Sustainable Scientific Software

### 2016-05-16 WSSSPE3/best_practices/main.tex
Update main.tex
updating affiliation

%
\thanks{{}$^{(1)}$ \hspace{-1ex}Center for Research Computing, University of Notre Dame, Notre Dame, IN, USA; sandra.gesing@nd.edu}
%
\thanks{{}$^{(2)}$ Mechanical and Aerospace Engineering, University at Buffalo, Buffalo, NY, USA; abani@buffalo.edu}
%
\thanks{{}$^{(3)}$ University of Illinois, IL, USA; d.katz@ieee.org}
%

>>>>

%
\thanks{{}$^{(1)}$ Center for Research Computing, University of Notre Dame, Notre Dame, IN, USA; sandra.gesing@nd.edu}
%
\thanks{{}$^{(2)}$ Mechanical and Aerospace Engineering, University at Buffalo, Buffalo, NY, USA; abani@buffalo.edu}
%
\thanks{{}$^{(3)}$ National Center for Supercomputing Applications (NCSA), Graduate School of Library and Information Science, and Electrical and Computer Engineering, University of Illinois, Urbana-Champaign, IL, USA; d.katz@ieee.org}
%
